\documentclass[../../dissertation.tex]{subfiles}
\begin{document}

The strong Church-Turing thesis, that states that any algorithmic process can
be simulated efficiently using a Turing Machine, was challenged by
\cite{solvaystrassen77} where they presented what is known as the
\textit{Solovay-Strassen primality test}. They showed that it is possible to
test whether a integer is prime or composite using a randomized algorithm. The
implication is that, because of the randomness, the Solvay-Strassen primality
test does not determine with certainty whether a integer is prime or composite,
rather it computes that a number is \textit{probably} prime or else
\textit{certainly} composite. This is of significance since no deterministic
test for primality was known at the time (nor it is now), meaning that this was
an example of a class of problems that could not be efficiently solved by a
conventional deterministic Turing Machine.\par

%TODO: Talvez exemplos diferentes?  TODO: Quicksort faz sentido quando tamos a
%falar do monte carlo?
This led to a modification of the Church-Turing thesis, now stating that any
algorithm can be simulated efficiently using a \textit{probabilistic} Turing
machine. The discovery of more instances of such algorithms followed,
\cite{motwani1995} and \cite{papadimitrious1994} show several problems that can
be solved based on randomized algorithms. For example, the \textit{Quicksort}
algorthim, developed by \cite{hoare61}, has a high probability of finishing in
$O(n \log{n})$. In contrast to many deterministic algorithms that require
$O(n^2)$ time. They also show algorithms that take advantage of \textit{Markov
chains} and the \textit{Monte Carlo method}. The volume of a convex body,
proposed by \cite{dyer1991}, can be estimated by a randomized algorithm in
polynomial time; the permanent of a nonnegative entry matrix can also be
approximately calculated in probabilistic polynomial time as was shown by
\cite{jerrum2001} and the \textit{k-SAT} and satisfiability with restrictions
problem by \cite{schoning1999}. \par

%TODO: Definicao da wikipedia um bocado fraca
Random walks, as the name suggests, belong to this class of algorithms.
\cite{kpearson1905} coined the term random walk, and they can be described as
path consisting of a succession of steps determined by a stochastic process,
over a mathematical space. They are a special case of \textit{Markov chains},
which are stochastic processes that assume discrete values and whose next state
is dictated by a deterministic or random rule based only on the current state.
This is a useful framework, since it can be used to explain the behaviour of
systems across many fields, from the Brownian movement of particles moving
through a gas, to the price of a fluctuating stock as shown by
\cite{cootner67}.\par

The quantum analogue of the random walk was firstly developed by
cite{aharonov1993}, where they defined the \textit{coined quantum random walk}.
This model consists of a walker and a coin that determines the movement of the
walker, which are both quantum systems where time is a discrete variable
dictated by the successive quantum coin flips and shifts in position.
\cite{nayak2000} presents the first analysis of the quantum walk on a graph
described by a line. Further work by \cite{inui2003} studies the behaviour of
the walk on grids and \cite{aharonov2002} on general graphs. 

\end{document}
